Reducing Linearizability of Priority Queues and More Data Structures to State Reachability

### 2017-02-20 data-independence-PQ.tex
move other part into appendix from Appendix B

A priority queue contains two method: $\textit{put}$ and $\textit{rm}$. A $\textit{put}$ method has two arguments, while the first argument is an item and the second argument is priority. A $\textit{put}$ method is used to put an item into the priority queue with certain priority. Here we assume that the item is chosen from a specific (possibly infinite) data domain $\mathbb{D}$ and priority is chosen from the set $\mathbb{N}$ of natural number. A $\textit{rm}$ method intends to remove the item with maximal priority in priority queue and then returns it. If the priority queue is empty, then $\textit{rm}$ returns $\textit{empty}$. If there are multiple items in priority queue with a same maximal priority, then $\textit{rm}$ will return the item that is putted earliest among such items. We say that $\textit{put}(a,p)$ matches $\textit{rm}(b)$, if $a = b$.

Let us slightly modify the notion of differentiated and data-independence in \cite{Wolper:1986} and propose data-differentiated sequence and data-independence for priority queues.

>>>>

Data-independence \cite{Wolper:1986} can be used to effectively handle unbounded data domain. In this section, we slightly modify the notion of data-independence in \cite{Wolper:1986} and propose data-differentiated sequences and data-independence for priority queues.

### 2017-02-20 rules-PQ.tex
move other part into appendix from Appendix B

>>>>

A priority queue contains two method: $\textit{put}$ and $\textit{rm}$. A $\textit{put}$ method has two arguments, while the first argument is an item and the second argument is priority. A $\textit{put}$ method is used to put an item into the priority queue with certain priority. Here we assume that the item is chosen from a specific (possibly infinite) data domain $\mathbb{D}$ and priority is chosen from the set $\mathbb{N}$ of natural number. A $\textit{rm}$ method intends to remove the item with maximal priority in priority queue and then returns it. If the priority queue is empty, then $\textit{rm}$ returns $\textit{empty}$. If there are multiple items in priority queue with a same maximal priority, then $\textit{rm}$ will return the item that is putted earliest among such items. We say that $\textit{put}(a,p)$ matches $\textit{rm}(b)$, if $a = b$.
